Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
rewrote the introduction

\section{Introduction}
Social interactions and attributes play a key role in software quality output 
from development teams~\cite{nagappan08,bettenburgh10}, these aspects have 
become more and more important and platforms that support software development 
processes provide every time a broader spectrum of measurements for social 
characteristics. Because of this we now have a wide variety of measurable social 
attributes that can be studied and analyzed to understand their correlation and 
impact on different success measures.

Similar studies in recent years have analyzed the relationship between social 
and technical factors using different measures of success~\cite{tsay14icse,tsay14fse}. 
This study aims to acknowledge the impact of some of these attributes when it 
comes to the quality of the commits developers write and its success when 
integrating into the project build through Travis CI.

>>>>

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.  However, to better understand successful 
project contributions, we must analyze factors which are common to all commits.

Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. One such
technique is continuous integration. Continuous integration automatically checks
the contribution against the project's test cases, to notify the development
team if the change caused a test case failure~\cite{Meyer14}.  When a change
passes one of these vetting techniques, it shows that the project developers
have confidence in the changes.

In past studies, both technical factors and social factors have been found to be
important when when predicting pull request success~\cite{tsay14icse,tsay14fse}.
Yet, these factors may not be as important during continuous integration.
Specifically, we want to investigate if social factors, which can be used a
proxy for experience, are important when predicting build success when grouped
with technical data, used as a proxy for commit complexity.
